% This is main.tex, a sample paper demonstrating the use of the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
% 
\documentclass[runningheads]{llncs}
\usepackage[a4paper,left=3cm,right=3cm,top=4cm,bottom=4cm,bindingoffset=5mm]{geometry}
%
% ---- Packages ----
%
\usepackage{graphicx} % enhanced support for graphics
\usepackage{url} % add macros for handling URLs in text
\usepackage[nohyperlinks,nolist]{acronym} % abbreviation utilities
\usepackage{listings}
\usepackage{float}
\usepackage{tabularx}
% TODO: add more packages below if necessary
%
% ---- Acronyms ----
%
\begin{acronym}
\acro{rq}[RQ]{Research Question}
% TODO: define more acronyms here
\acro{llm}[LLM]{large language model}
\acro{lm}[LM]{language model}
\acro{sast}[SAST]{static application security testing}
\acro{ci}[CI]{continuous integration}
\acro{fn}[FN]{false negative}
\acro{fp}[FP]{false positive}
\acro{oss}[OSS]{open-source software}
\acro{rag}[RAG]{retrieval augmented generation}
\acro{cve}[CVE]{Common Vulnerabilities and Exposures}
\acro{bic}[BIC]{bug-inducing commit}
\acro{bfc}[BFC]{bug-fixing commit}
\end{acronym}
%
% ---- Begin Document ----
%
\begin{document}
%
\title{LLM-Augmented Static Analysis Security Testing}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
% ---- Author Information ----
%
\author{Murilo Escher Pagotto Ronchi}
\institute{Seminar: Software Quality\\
Advisor: Kohei Dozono\\
Technical University of Munich\\
\email{murilo.escher@tum.de}}
%
\maketitle % typeset the header of the contribution
%
% ---- Abstract ----
%
\begin{abstract}
Static Application Security Testing (SAST) tools are widely used to detect vulnerabilities in software systems by analyzing source code, bytecode, or binaries. However, these tools often face limitations, including false positives and difficulties in analyzing vulnerabilities caused by runtime behavior. Recent advancements in large language models (LLMs) have demonstrated their potential to enhance software security analysis, particularly when combined with traditional SAST tools.

This paper explores the integration of SAST tools with LLMs to address these limitations. By leveraging the BugOSS dataset—a collection of open-source projects with documented vulnerabilities—this study employs CodeQL and Infer to analyze vulnerabilities and gathers additional context through call graph analysis. The contextual data, including caller and callee relationships, is combined with SAST output and formatted into structured prompts for GPT-4. This approach aims to reduce false positives and improve the reasoning behind vulnerability detection.

The results reveal that while LLMs excel in reasoning about simpler vulnerabilities like null pointer dereferences, their performance diminishes for more complex issues requiring deeper code comprehension. While contextual information provided valuable insights into the code structure, its overall impact on reducing false positives was limited, as many flagged vulnerabilities were isolated or lacked meaningful interdependencies in the call graph. These findings highlight both the potential and the limitations of LLM-augmented static analysis, laying the groundwork for future research on integrating richer program representations with LLMs for enhanced security testing.

\keywords{Security testing  \and Static analysis \and Large language models.}
\end{abstract}
%
% ---- Text Parts ----
%
\input{text/01_introduction.tex}
\input{text/02_related_work.tex}
\input{text/03_approach.tex}
\input{text/04_evaluation.tex}
\input{text/05_conclusion.tex}
%
% ---- Appendix ----
%
\appendix
% \input{text/99_appendix}
%
% ---- Bibliography ----
%
\bibliographystyle{splncs04}
\bibliography{library.bib}
%
\end{document}